$<$D\+ZA\mbox{[}afk\mbox{]}$>$ Dev\+IL song\+: "la la la, a cross-\/platform image library utilizing a simple syntax to load, save, convert, manipulate, filter and display a variety of images with ease, la la la"

\subsection*{What is it? }

Dev\+IL is an Open Source image library whose distribution is done under the terms of the G\+NU L\+G\+PL license. See the C\+O\+P\+Y\+I\+NG file for more details. Dev\+IL offers you a simple way to implement loading, manipulating, filtering, converting, displaying, saving from/to several different image formats in your own project.

\subsection*{Where can I find it? }

Dev\+IL can be found at \href{http://openil.sourceforge.net}{\tt http\+://openil.\+sourceforge.\+net}

\subsection*{How do I build and install the 3 libraries ? }

C\+Make is used to handle building Dev\+IL across multiple platforms.

See R\+E\+A\+D\+M\+E.\+cmake for details.

\subsection*{More Extensive Documentation }

This file is only a quick guide to point you to more detailed information on how to use Dev\+IL. More extensive documentation can currently be found on the Dev\+IL site at \href{http://openil.sf.net}{\tt http\+://openil.\+sf.\+net} and in the /\+Docs directory in a normal install.

\subsection*{Why the hell another image library? }

I have never seen an image library that can do everything Dev\+IL does. Sure, various different libraries can do part of what Dev\+IL can do as well or even better, but I wanted a simple to use library that encompassed all of these features. I also wanted an extremely portable image library that could be used from a variety of languages and utilized the Open\+GL syntax.

\subsection*{Basic Readme }

Most anything stated in this document applies to Dev\+IL as well as Dev\+I\+LU and Dev\+I\+L\+UT, unless otherwise stated. (This file is best viewed with word wrap on.)

\subsection*{Errors\+: }

All errors generated inside Dev\+IL, along with illegal parameters passed to Dev\+IL functions are caught and passed to il\+Set\+Error(), an internal library function. The calling program can call \hyperlink{il_8h_add4600e363a1e68cf5f5e34e5bce5bac}{il\+Get\+Error()} to get the value of the error generated. Error types are defined in \hyperlink{il_8h}{il.\+h}, using the 0x501 -\/ 0x5\+FF range. \hyperlink{il_8h_add4600e363a1e68cf5f5e34e5bce5bac}{il\+Get\+Error()} will return 0 (I\+L\+\_\+\+N\+O\+\_\+\+E\+R\+R\+OR) if no error has occurred.

\subsection*{Basic Usage\+: }

This demonstrates loading an image through Dev\+IL for Open\+GL. Don\textquotesingle{}t forget to call il\+Init before you before you do anything\+:

\#include $<$\hyperlink{il_8h}{I\+L/il.\+h}$>$ \#include $<$\hyperlink{ilu_8h}{I\+L/ilu.\+h}$>$ \#include $<$\hyperlink{ilut_8h}{I\+L/ilut.\+h}$>$

...

I\+Luint devil\+Error;

il\+Init();

devil\+Error = \hyperlink{il_8h_add4600e363a1e68cf5f5e34e5bce5bac}{il\+Get\+Error()};

if (devil\+Error != I\+L\+\_\+\+N\+O\+\_\+\+E\+R\+R\+OR) \{ printf (\char`\"{}\+Devil Error (il\+Init\+: \%s\textbackslash{}n\char`\"{}, ilu\+Get\+Error\+String (devil\+Error)); exit (2); \}

....

I\+Luint devil\+ID;

il\+Gen\+Images(1, \&devil\+I\+D); il\+Bind\+Image(devil\+I\+D); il\+Load\+Image(\char`\"{}default1.\+tga\char`\"{}); // Loads into the current bound image devil\+Error = \hyperlink{il_8h_add4600e363a1e68cf5f5e34e5bce5bac}{il\+Get\+Error()};

if (devil\+Error != I\+L\+\_\+\+N\+O\+\_\+\+E\+R\+R\+OR) \{ printf (\char`\"{}\+Devil Error (il\+Load\+Image\+: \%s\textbackslash{}n\char`\"{}, ilu\+Get\+Error\+String (devil\+Error)); exit (2); \}

....

ilut\+Renderer(\+I\+L\+\_\+\+O\+P\+E\+N\+G\+L); // Switch the renderer

....

G\+Luint opengl\+ID, opengl\+Error;

opengl\+ID = ilut\+G\+L\+Bind\+Tex\+Image(); // This generates the texture for you devil\+Error = \hyperlink{il_8h_add4600e363a1e68cf5f5e34e5bce5bac}{il\+Get\+Error()};

if (devil\+Error != I\+L\+\_\+\+N\+O\+\_\+\+E\+R\+R\+OR) \{ printf (\char`\"{}\+Error\+: \%s\textbackslash{}n\char`\"{}, ilu\+Get\+Error\+String (devil\+Error)); exit (2); \}

if (opengl\+Error != G\+L\+\_\+\+N\+O\+\_\+\+E\+R\+R\+OR) \{ printf (\char`\"{}\+Opengl Error (ilut\+G\+L\+Bind\+Tex\+Image)\+: \%s\textbackslash{}n\char`\"{}, glu\+Get\+Error\+String (opengl\+Error)); exit (2); \}

// Make sure to close the image when you are done with it (though Dev\+IL // automatically deletes them when the program exits)\+:

gl\+Delete\+Textures(1, \&opengl\+I\+D); il\+Delete\+Images (1, \&devil\+ID);

\subsection*{More Examples\+: }

The Test\+IL project is included to test features of Dev\+IL.

Dev\+IL includes a project called G\+L\+Test. This is a simple test of Dev\+IL\textquotesingle{}s capabilities. All it does it load any image and displays it in a window created by Free\+Glut, which is available on \href{http://freeglut.sourceforge.net}{\tt http\+://freeglut.\+sourceforge.\+net}. It is also included to let the user have an idea of what the library can really be used for.

Several other test projects are included to test support with various display A\+P\+Is. The Windows\+Test project is a basic image program that only runs in Windows right now but showcases several of Dev\+IL\textquotesingle{}s features through various menus.

If you want more in-\/depth tutorials, you can find them on \href{http://openil.sf.net,}{\tt http\+://openil.\+sf.\+net,} or they may be in your installation under the /examples directory. Documents are also available in the /docs directory.

\subsection*{Additional Reading }

All image formats used in Dev\+IL have corresponding documents on \href{http://www.wotsit.org,}{\tt http\+://www.\+wotsit.\+org,} under the Graphics Files section. These documents proved invaluable for the creation of this library when there was no library already available for that image format.

\subsection*{Legalese }

All contents of this file are intellectual property of Denton Woods, copyright 2001-\/2008. 